### 2021-05-16 paper/ms.tex
small amount of work

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[entropy,article,submit,moreauthors,pdftex]{Definitions/mdpi}

% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, analytica, animals, antibiotics, antibodies, antioxidants, appliedchem, applmech, applmicrobiol, applnano, applsci, arts, asi, atmosphere, atoms, audiolres, automation, axioms, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomechanics, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, brainsci, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coatings, colloids, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, crops, cryptography, crystals, curroncol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entropy, environments, environsciproc, epidemiologia, epigenomes, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forensicsci, forests, fractalfract, fuels, futureinternet, futuretransp, futurepharmacol, futurephys, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, land, languages, laws, life, liquids, literature, livers, logistics, lubricants, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, metabolites, metals, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, minerals, mining, modelling, molbank, molecules, mps, mti, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photochem, photonics, physchem, physics, physiolsci, plants, plasma, pollutants, polymers, polysaccharides, proceedings, processes, prosthesis, proteomes, psych, psychiatryint, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, systems, taxonomy, technologies, telecom, textiles, thermo, tourismhosp, toxics, toxins, transplantology, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wevj, women, world

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2021}
\copyrightyear{2021}
%\externaleditor{Academic Editor: Firstname Lastname} % For journal Automation, please change Academic Editor to "Communicated by"
\datereceived{} 
\dateaccepted{} 
\datepublished{} 
\hreflink{https://doi.org/} % If needed use \linebreak
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, paracol, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Forklift: An Implementation of Nested Sampling for Two Objective Functions}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Forklift}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Brendon J. Brewer $^{1}$}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Brendon Brewer}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Brewer, B. J.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address[1]{$^{1}$Department of Statistics, The University of Auckland,
Private Bag 92019, Auckland 1142, New Zealand; bj.brewer@auckland.ac.nz}

% Contact information of the corresponding author
%\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{I introduce {\em Forklift}, an implementation of Nested Sampling (NS)
that broadens its applicability to problems with two objective functions.
Such problems arise frequently in statistical mechanics, and occasionally in
Bayesian inference.}

% Keywords
\keyword{nested sampling; bayesian inference; monte carlo; statistical mechanics; multi-objective optimization}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}  %lol

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{Instead of the abstract}
%\entrylink{The Link to this entry published on the encyclopedia platform.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}

The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Histories, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
\begin{quote}
This is an example of a quote.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}
\item	First bullet;
\item	Second bullet;
\item	Third bullet.
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}
\item	First item; 
\item	Second item;
\item	Third item.
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.

\begin{figure}[H]
\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}

% The MDPI table float is called specialtable
\begin{specialtable}[H] 
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
%%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabular}
\end{specialtable}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

Text.

Text.

\subsection{Formatting of Mathematical Components}

This is the example 1 of equation:
\begin{equation}
a = 1,
\end{equation}
the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

This is the example 2 of equation:
\end{paracol}
\nointerlineskip
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
\end{equation}

% Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, \linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.
\begin{figure}[H]	
\widefigure
\includegraphics[width=15 cm]{Definitions/logo-mdpi}
\caption{This is a wide figure.\label{fig2}}
\end{figure}  
\begin{paracol}{2}
\linenumbers
\switchcolumn

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

\institutionalreview{In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals. Please note that the Editorial Office might ask you for further information. Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals. You might also choose to exclude this statement if the study did not involve humans or animals.}

\informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.

Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}. You might choose to exclude this statement if the study did not report any data.}

\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the~results''.}

%% Optional
\sampleavailability{Samples of the compounds ... are available from the authors.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & Linear dichroism
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section{}
\subsection{}
The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

\begin{specialtable}[H] 
%\tablesize{\scriptsize}
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab2}}
%\tablesize{} % You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabular}
\end{specialtable}

\section{}
All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{paracol}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
\bibitem[Author2(year)]{ref-book1}
Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
% Reference 3
\bibitem[Author3(year)]{ref-book2}
Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
% Reference 4
\bibitem[Author4(year)]{ref-unpublish}
Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} stage of publication (under review; accepted; in~press).
% Reference 5
\bibitem[Author5(year)]{ref-communication}
Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
% Reference 6
\bibitem[Author6(year)]{ref-proceeding}
Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of Presentation. In Title of the Collected Work (if available), Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference; Editor 1, Editor 2, Eds. (if available); Publisher: City, Country, Year (if available); Abstract Number (optional), Pagination (optional).
% Reference 7
\bibitem[Author7(year)]{ref-thesis}
Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
% Reference 8
\bibitem[Author8(year)]{ref-url}
Title of Site. Available online: URL (accessed on Day Month Year).
\end{thebibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2021-05-16 paper/ms.tex
Text dump from old draft

@@
 The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, paracol, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{dsfont}
+\newcommand{\xx}{\boldsymbol{\theta}}
+\newcommand{\dx}{d\boldsymbol{\theta}}
+\newcommand{\data}{D}
+\newcommand{\II}{I}
+\newcommand{\mnras}{Monthly Notices of the Royal Astronomical Society}
+\newcommand{\todo}{\color{blue}{\bf TODO}:~}
 
@@
 that broadens its applicability to problems with two objective functions.
-Such problems arise frequently in statistical mechanics, and occasionally in
-Bayesian inference.}
+I demonstrate the algorithm on three example problems:
+(i) a toy problem whose partition function $Z(\beta_1, \beta_2)$ (of two
+temperatures) is known, so we can compute the actual error in the reconstructed
+function $Z(\beta_1, \beta_2)$; (ii) a collection of atoms with a potential
+that is intermediate between a Lennard-Jones form and a `polymer' form; and
+(iii) {\todo decide between a few options: image reconstruction with an
+intractable normalizing constant in the prior, or perhaps the `Potts' example
+which is a compromize between a 2D potts model and a product of many 1D
+Potts models}.
+A free software implementation in modern C++ is available at
+\url{https://github.com/eggplantbren/Forklift}.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\setcounter{section}{-1} %% Remove this when starting to work on the template.
-\section{How to Use this Template}
-
-The template details the sections that can be used in a manuscript.
-Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section).
-Please check the instructions on the authors' page of the journal to verify the correct order and names.
-For any questions, please contact the editorial office of the journal or support@mdpi.com.
-For LaTeX-related questions please contact latex@mdpi.com.
-%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
-
-\section{Introduction}
-
-The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{ref-journal}.
-Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
-Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Histories, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods}
+\begin{document}
+\section{Nested Sampling}
 
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
+Nested Sampling (NS) \citep{skilling2006nested} is general
+Monte Carlo algorithm that can solve a wide range of problems in Bayesian
+computation, statistical mechanics, and information theory
+\citep[e.g.][]{partay2010efficient, exoplanet, baldock2016determining,
+brewer2017computing}.
+Its key strength its ability to cope with phase transitions and other
+features which cause problems for many other methods such as those based
+on `annealing' \citep{neal2001annealed}. These methods all fall into that half
+of the Monte Carlo landscape that addresses {\em what distribution to sample}
+rather than how to sample it.
 
-Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
+In a Bayesian inference problem with unknown parameters denoted collectively
+by a vector $\xx$, the
+posterior distribution for the parameters given a data proposition $\data$ and
+a `prior information' proposition $\II$ is:
+\begin{eqnarray}
+p(\xx | \data, \II) &=&
+\frac{p(\xx | \II)p(\data | \xx, \II)}{p(\data | \II)}\\
+&=& \frac{\pi(\xx)L(\xx)}{Z}
+\end{eqnarray}
+where $\pi(\xx)$ is the prior distribution, $L(\xx)$ is the likelihood
+function, and $Z$ is the normalising constant, known as the
+`marginal likelihood' or `evidence':
+\begin{eqnarray}
+Z &=& \int \pi(\xx) L(\xx) \, \dx.\label{eqn:evidence}
+\end{eqnarray}
 
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
-\begin{quote}
-This is an example of a quote.
-\end{quote}
+$Z$ is useful because it is the prior probability of the data conditional on
+the hypothesis that $\xx$ is {\em one of}
+the possibilities in the space being integrated over, along with
+whatever additional assumptions were made. $Z$ thus plays the role
+of a likelihood for the parameter space as a whole, and is a key input in
+calculating the posterior probabilities of competing `models' (mutually
+exclusive choices of $\II$).
+Naively, Equation~\ref{eqn:evidence} appears straightforward to compute because
+it is a simple expectation of $L$ with respect to the distribution $\pi$.
+However,
+NS is required because Equation~\ref{eqn:evidence}
+is the expected value of $L$ with respect to a very heavy-tailed distribution
+(the distribution of $L$-values implied by $\pi(\xx)$). This means a very
+large number of samples would be required.
+Hence, there is a strong
+connection between NS and ideas from rare event simulation
+(\citet{walter2017point} has explicitly explored this connection).
+Another way of thinking about this
+challenge is that the $Z$ integral is dominated by a region with very
+high values of $L$ but very low probability according to $\pi$ (and usually
+very low volume according to $d\xx$, as well).
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+The main goal of NS is to compute $Z$, but it can also be used to make
+Monte Carlo approximations of the posterior distribution, and to
+calculate the `information',
+or Kullback-Leibler divergence from the prior to the posterior:
+\begin{eqnarray}
+H &=& \int p(\xx | \data, \II) \log
+\left(\frac{p(\xx | \data, \II)}{p(\xx | \II)}\right) \, d\xx \\
+&=& \int \frac{\pi(\xx) L(\xx)}{Z} \log
+\left(\frac{L(\xx)}{Z}\right) \, d\xx.
+\end{eqnarray}
+$H$ quantifies how compressed the posterior distribution is with
+respect to the prior. For example, $H = 100$ nats (the units obtained when
+the logarithm is the natural logarithm) implies, loosely speaking,
+that the posterior is to be found in a tiny region of the space that
+has a prior probability of only $e^{-100}$.
+$H$ can be interpreted quite literally as a measure of how much
+the specific data $\data$ resolved the question ``what is the value
+of $\xx$, precisely?'' \citep{knuth_questions, van2017inquiry}.
+\citet{brewer2017computing} introduced a version of NS that computes
+Shannon entropies, including entropies of marginal distributions (whereas
+standard NS can only compute divergences for full joint distributions).
 
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-\subsection{Subsection}
-\subsubsection{Subsubsection}
+NS works by drawing particles from the
+prior $\pi(\xx)$ and successively imposing constraints on the value of
+the likelihood $L(\xx)$ that compress the prior mass by a (roughly) known
+and constant factor. Like related algorithms such as those
+based on `annealing' or `tempering', NS
+moves through a sequence of probability distributions, beginning with the
+prior. It is the specific sequence of distributions used that distinguishes
+NS from annealing. The sequence of distributions used in NS is defined by
+\begin{eqnarray}
+p(\xx; \ell) &=& \frac{1}{X(\ell)}\pi(\xx)\mathds{1}\left(L(\xx) > \ell\right).
+\label{eq:constrained_prior}
+\end{eqnarray}
+where $X(\ell) = \int \pi(\xx)\mathds{1}\left(L(\xx) > \ell\right)$ is the
+normalising constant of the distribution constrained by the condition
+$L(\xx) > \ell)$. $X$ is also the quantile function of the likelihoods.
 
-Bulleted lists look like this:
-\begin{itemize}
-\item	First bullet;
-\item	Second bullet;
-\item	Third bullet.
-\end{itemize}
+The marginal likelihood can be computed by numerically integrating the
+function $L(X)$:
+\begin{eqnarray}
+Z &=& \int_0^1 L(X)\, dX.
+\end{eqnarray}
+\citet{salomone2018unbiased}
+recently showed how NS can be viewed as an instance of
+Sequential Monte Carlo (SMC), with a particular choice of the sequence of
+distributions. By weighting the sequence of discarded points differently from
+Skilling, the estimates of $Z$ are unbiased.
 
-Numbered lists can be added as follows:
+%Throughout this paper we use the popular `overloaded' notation for some
+%functions and probability distributions.
+%For example, $L(\xx)$ is the likelihood function, and $L(X)$ is the likelihood
+%as a function of the enclosed prior mass $X$. The inverse, $X(L)$, takes a
+%likelihood as input and computes the corresponding enclosed prior mass.
+%Therefore the symbol $L$ implies the output of the function is a
+%likelihood value; so $L(\xx)$ represents a likelihood value computed from
+%the parameters $\xx$, and $L(X)$ represents a likelihood value that
+%corresponds to an amount $X$ of prior mass. In more traditional notation,
+%$X(L)$ would be written using function composition, $X(L(\xx))$.
+
+\section{Accessing distributions other than the posterior}
+Using a single NS run, we can also calculate the properties of any
+distribution that
+is (in some sense which we do not make precise) {\em intermediate}
+between the prior and the posterior. For example, we might be interested in
+a `power posterior' where the likelihood is raised to a power $\beta$
+(this is also the family of distributions used in `annealing' or `tempering'
+methods):
+\begin{eqnarray}
+p(\xx; \beta) &=& \frac{\pi(\xx)L(\xx)^\beta}
+                       {Z(\beta)}\label{eqn:power_posterior}
+\end{eqnarray}
+The normalisation and posterior samples from this distribution can be obtained
+from the original NS run by re-weighting the output according to $L(\xx)^\beta$
+instead of the usual $L(\xx)$ used to obtain the posterior.
+Bayesian inference problems with `gaussian noise' likelihood assumptions
+provide an example of where power posteriors might be useful.
+Computing $p(\xx; \beta)$ for $\beta \neq 1$ allows us to explore what the
+posterior distribution would have been if the noise variance had been greater,
+without having to re-run the algorithm.
+This is different from including an extra parameter to allow the noise variance
+to be greater, because NS allows you to test the consequences of values of the
+variance that are very implausible given the data, i.e. that do not have
+a high posterior probability.
+
+Alternatives to NS include methods based on `annealing', where a sequence of
+distributions of the form of Equation~\ref{eqn:power_posterior} is used.
+There are many different methods based on this idea, such as the popular
+parallel tempering \citep{hansmann1997parallel, gregory2005bayesian},
+simulated tempering \citep{marinari1992simulated},
+annealed importance sampling \citep{neal2001annealed}, and
+steppingstone sampling \citep{xie2010improving}.
+However, unlike annealing methods, NS requires only a small number of
+tuning parameters (just the number of particles $N$ is inherent to NS, although
+most NS implementations have additional tuning parameters related to their
+methods for sampling Equation~\ref{eq:constrained_prior}). Annealing methods
+also tend to fail on phase change problems \citep{skilling} which can arise
+in data analysis \citep{rjobject, exoplanet} as well as in statistical
+mechanics, where they are more familiar.
+
+In statistical mechanics, Equation~\ref{eqn:power_posterior} defines the
+family of {\it canonical distributions}, usually written as:
+\begin{eqnarray}
+p(\xx; \beta) &=& \frac{\pi(\xx)\exp[-\beta E(\xx)]}{Z(\beta)}
+\end{eqnarray}
+where $E(\xx)$ is the energy function (analogous to minus the log likelihood
+in the Bayesian case), and $\pi(\xx)$ is often uniform over
+phase space (the set of possible positions and momenta of a collection of
+particles) or configuration space (the set of possible positions of a collection
+of particles).
+
+In this context we usually want to
+compute $Z(\beta)$ as a function of $\beta$, which is called the
+{\it partition function}. When the full phase space of positions and momenta
+is included, the KL-divergence as a function of temperature,
+$H(\beta)$, is the Gibbs entropy (up to a sign change and a constant factor).
+A single run of NS can be used to reconstruct $Z(\beta)$ and $H(\beta)$,
+allowing the study of
+the properties of materials from first principles, based on hypotheses about
+the atoms or molecules that make them up
+\citep[e.g.][]{partay2010efficient, baldock2016determining}.
+The NS exploration algorithm is invariant under
+monotonic transformations of $L$ or $E$ and therefore there we can discuss the
+algorithm in Bayesian or statistical mechanical terms without loss of
+generality.
+
+\subsection{Notation for Objective Functions}
+Throughout this paper we will refer to $L(\xx)$ or
+$-E(\xx)$ as `objective functions',
+by analogy with the terminology used in optimization.
+Although we are interested in sampling rather
+than optimization, we still want to increase the values of $L$ or decrease
+the values of $E$ relative to what is typical of the prior --- just in
+a controlled manner, so we can quantify prior mass as we ascend.
+
+Throughout this paper and the software, there are three
+conventions used to define the objective functions. $L()$ is named by analogy
+with likelihood, and appears multiplicatively as in
+Equation~\ref{eqn:power_posterior}. $E() = -\ln L()$ is named by analogy with
+`energy'. Finally, in the software,
+$S() = \ln L() = -E()$ is often used (the $S$ stands for a
+`{\em S}calar function of $\xx$'). The algorithm ascends $L$ and $S$, but
+descends $E$.
+
+\section{Multiple objective functions}
+In some inference and
+statistical mechanics problems, there are two or more scalar functions of
+$\xx$ that are relevant. Suppose our prior is $\pi(\xx)$ as before, and
+we obtain information that fixes the expected values of two scalar
+``likelihood'' functions of $\xx$, $L_1(\xx)$ and $L_2(\xx)$
+(or equivalently, ``energy'' functions $E_1(\xx) = -\ln L_1(\xx)$ and
+$E_2 = -\ln L_2(\xx)$). The
+updated probability distribution that takes into account the constraints is
+of the canonical form \citep{jaynes1957information}:
+\begin{align}
+p(\xx; \beta_1, \beta_2) &=
+    \frac{\pi(\xx)L_1(\xx)^{\beta_1}L_2(\xx)^{\beta_2}}
+         {Z(\beta_1, \beta_2)} \\
+    &=
+    \frac{\pi(\xx)\exp\left[-\beta_1E_1(\xx) - \beta_2E_2(\xx)\right]}
+         {Z(\beta_1, \beta_2)}
+\end{align}
+where $\beta_1$ and $\beta_2$ are two `inverse temperatures' (the temperatures
+themselves are $T_1 = \beta_1^{-1}$ and $T_2 = \beta_2^{-1}$).
+In a Bayesian
+context, this distribution (when $\beta_1 = \beta_2 = 1$) could be the
+posterior distribution for parameters $\xx$
+given two datasets, where $L_1$ and $L_2$ are the
+likelihood functions for each dataset. In statistical mechanics, $E_1$ might
+be the total energy and $E_2$ might be the total
+angular momentum, or perhaps a term depending on an external field (so $\beta_2$
+would then describe the strength of the external field).
+
+If we are only interested in a single canonical distribution, for example
+with $\beta_1 = 0.3$ and $\beta_2 = 0.7$, we can estimate its normalising
+constant and by running standard Nested Sampling with objective function
+$L(\xx) = L_1(\xx)^{\beta_1}L_2(\xx)^{\beta_2}$. However, what if we
+are interested in a range of values for $\beta_1$ and $\beta_2$, and we
+want to know the entire partition function $Z(\beta_1, \beta_2)$?
+This work describes
+progress towards solving this class of problems while maintaining the benefits
+of Nested Sampling, such as the ability to cope with phase
+transitions. The algorithm is presented here for problems with two objective
+functions, but the implementation allows for more than two (though the
+performance is those cases is likely to be poor).
+
+\section{Algorithm requirements}
+The prior $\pi(\xx)$ implies a certain prior for $L_1$ and $L_2$, which we
+denote $\pi(L_1, L_2)$, overloading the $\pi$ symbol.
+An example of a prior is shown as the
+probability density in Figure~\ref{fig:joint1}. The partition function
+$Z(\beta_1, \beta_2)$ is a set of expected values with respect to this density.
+By analogy with the standard case of one objective function,
+simple Monte Carlo sampling from $\pi$ will not work except for values of
+$(\beta_1, \beta_2)$ where the canonical distributions of interest are
+not too different from $\pi$.
+We need a sampler that explores regions where $L_1$ and $L_2$ are increased
+(relative to what's typical of $\pi$) in order
+to accurately estimate $Z(\beta_1, \beta_2)$. The specific way of increasing
+$L_1$ and $L_2$ should follow the requirements listed in the following
+subsection, which are unique to NS. Another unique property of NS which our
+algorithm {\em does not} satisfy is discussed in Appendix~\ref{sec:property}.
+
+\subsection{Desiderata}
+While we could not see how to satisfy the property in
+Appendix~\ref{sec:property},
+the algorithm of this paper does satisfy the following other NS properties:
 \begin{enumerate}
-\item	First item; 
-\item	Second item;
-\item	Third item.
+\item It begins with $N$ points drawn from the prior $\pi(\xx)$.
+\item It seeks to explore regions where the values of
+$L_1(\xx)$ and $L_2(\xx)$ are higher than the prior $\pi(L_1, L_2)$
+would typically imply.
+\item It considers a sequence of probability
+distributions proportional to $\pi$, but restricted to smaller and smaller
+domains for which the enclosed prior mass shrinks by a (roughly) constant and
+known factor at each iteration.
+\item The exploration procedure is invariant under monotonic transformations of
+$L_1$ and $L_2$, i.e. it should only depend on rankings of $L_1$ and $L_2$
+values and not on the numeric values themselves.
 \end{enumerate}
+The standard Nested Sampling algorithm has these properties but for a
+single objective function. The same is true of variants such as
+Diffusive Nested Sampling \citep{dns, dnest4} and PolyChord
+\citep{handley2015polychord}.
 
-The text continues here.
+\subsection{The algorithm}
+The algorithm itself is rather simple. It consists of a collection of
+{\em reps} (short for repetitions) of Nested Sampling, each of which ascends
+a different compromise between $L_1$ and $L_2$. The output of the reps can then
+be used, with appropriate weights, to represent canonical distributions at
+any temperature.
 
-\subsection{Figures, Tables and Schemes}
+The combination of the reps makes use of the (approximate?) unbiasedness
+property of Nested Sampling when the prior weights of the dead particles are
+assigned proportional to
+$[(N-1)/N]^i$ at iteration $i$, instead of being based on
+Skilling's geometric sequence of $X$-values given by $\exp(-i/N)$.
+\citet{walter2017point} demonstrated that the Nested Sampling estimator of $Z$
+is unbiased with these weights, but assuming perfect sampling of the replacement
+particles at each iteration. Additionally, using the framework of
+Sequential Monte Carlo \citep{doucet2001introduction},
+\citet{salomone2018unbiased} showed that this remains true even if imperfect
+MCMC is used to generate new particles. Technically, this property is
+lost if the sequence of distributions is chosen adaptively (a key feature of NS)
+rather than being fixed in advanced. However, this paper demonstrates that the
+algorithm works well in practice despite this limitation.
+{\todo Verify/prove statement about bias, and that it means I can average
+reps the way I'm doing it. Also check this remains the case with the random
+thinning that I'm using.}
 
-All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
+The fact that $Z$ estimates can be made unbiased means that separate $Z$
+estimates can be averaged together and the properties of the averaged estimator
+will be easily understood and satisfactory ({\todo probably need to be more
+technical here.}). {\todo The following statement is based on intuition}
+Runs that ascend the `wrong' objective function are still unbiased
+estimates of $Z$ for the `right' objective function. Some of the reps will
+be well-positioned to represent some canonical distributions but inappropriate
+for others. When this happens, the particles from the rep will just have very
+low weights with respect to some canonical distributions.
 
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
-\caption{This is a figure.
-Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.\label{fig1}}
+{\todo A description of the algorithm for a single rep follows}.
+For each rep, we set up a probability distribution over the objective functions,
+given by probabilities $\boldsymbol{p} = \{p_1, ..., p_n\}$,
+where $n$ is the number of
+objective functions. If there
+are only two objective functions, there is just a probability $p_1$ for
+objective function 1, and $p_2 = 1-p_1$ for objective function 2.
+
+The first distribution is the prior $\pi(\xx)$. Objective function thresholds
+$(\ell_1, \ell_2)_0 = (-\infty, -\infty)$ are assigned.
+$N$ particles are generated
+from the prior. Then, an objective function is selected according to the
+probability distribution $\boldsymbol{p}$.
+Suppose the objective function chosen is number $k$.
+Then the worst particle wrt that criteron is written to disk and replaced,
+and the threshold is updated in the $k$th position only.
+
+Essentially, a `rep' is just Nested Sampling, but where a threshold is
+maintained for all objective functions. At each iteration, the space is
+restricted by the value of only one of the objective functions.
+
+The probability distribution $\boldsymbol{p}$ influences the
+proportion of the compressions that are done using each objective function.
+Different reps ought to have different values for the probability distribution.
+Some reps will mostly increase $L_1$, some will mostly increase $L_2$, and
+some will be in between. In the reference implementation
+(Appendix~\ref{sec:software}), the log-probabilities are chosen from a $t$
+distribution with 2 degrees of freedom, exponentiated, and then normalized.
+
+\begin{algorithm}[!ht]
+    \setstretch{1.35}
+    Set $N$, the number of particles \\
+    Set $M$, the number of reps \\
+    Set $d$, the target depth in nats \\
+    Compute $J = Nd$, the number of NS iterations per rep \\
+    \For{i in 1:$M$}{
+      Set initial threshold $(\ell_1^*, \ell_2^*) = (0, 0)$ \\
+      Generate initial particles $(\xx_1, ..., \xx_N)$ from prior $\pi$ \\
+      Generate a `direction' (probability distribution over objective functions) $\boldsymbol{p}$ \\
+      \For{j in 1:$J$}{
+          Choose an objective function $k$ according to $\boldsymbol{p}$ \\
+          Find $c = \textnormal{argmin}(\lambda C \to L_k(\xx_C))$, the index of the worst particle \\
+          Write out $\xx_c$ to disk as $\xx_{ij}$ with prior weight $w_{ij}$ proportional to $(1 - 1/N)^j$ \\
+          Replace threshold element $\ell_c^*$ with $L_k(\xx_c)$ \\
+          Replace particle $c$ with new particle generated from
+            $\pi\times\mathds{1}(L_1 > \ell_1^*, L_2 > \ell_2^*)$          
+      }
+    }
+
+    Set $(T_1, T_2)$, the temperatures of a canonical distribution of interest \\
+    Compute $\hat{Z}(T_1, T_2) \leftarrow \left(\sum_{ij} w_{ij}L_1(\xx_{ij})^{1/T_1}L_2(\xx_{ij})^{1/T_2}\right) / \sum_{ij} w_{ij}$\\
+  \vspace*{0.5em}
+  \caption{The `Switch Sampling' algorithm.}
+\end{algorithm}
+
+\section{Example 1: Known solution}
+In the software repository, this example is implemented in
+{\tt examples/Demo.h} and {\tt examples/Demo.cpp}.
+We tested the algorithm on a simple 100-dimensional example, where the
+prior is a uniform distribution between 0 and 1 for each coordinate:
+\begin{eqnarray}
+\pi(\xx) &=& \prod_{i=1}^{100}
+\left\{
+\begin{array}{lr}
+1, & x_i \in [0, 1]\\
+0, & \textnormal{otherwise.}
+\end{array}
+\right.
+\end{eqnarray}
+The first objective function is quadratic in form, such that the canonical
+distributions are iid normal centered at $(0.5, 0.5, ..., 0.5)$:
+\begin{eqnarray}
+E_1(\xx) &=& \sum_{i=1}^{100} \left(\frac{x_i - 0.5}{0.1}\right)^2.
+\end{eqnarray}
+The second objective function, given by
+\begin{eqnarray}
+E_2(\xx) &=& \sum_{i=1}^{100}\sin^2(10 \pi x_i),
+\end{eqnarray}
+upweights states where coordinates $\{x_i\}$
+are close to 0, 0.1, 0.2, ..., 0.9 and 1.
+Since both of the objective functions are simple sums over the coordinates,
+the canonical distributions are products of independent distributions for
+each coordinate.
+
+The canonical distributions for this system should draw the coordinates
+towards 0.5 (due to $E_1$) and towards the troughs of $E_2$, with the
+relative importance of these effects determined by the values of the
+inverse temperatures $\beta_1$ and $\beta_2$. Three example canonical
+distributions are shown in Figure~\ref{fig:demo_canonical}.
+The true partition function (computed numerically) and the Kullback-Leibler
+divergence from the prior to the canonical distribution are shown in
+Figure~\ref{fig:demo_truth} as a function of two temperatures. These show the
+common behaviour where lower temperatures correspond to lower values
+of the normalising constant $\log Z$ and higher values of the KL divergence
+$H$. There are no phase changes, which would result in discontinuities.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[scale=0.6]{figures/demo_canonical.pdf}
+\caption{Three canonical distributions for different values of the two
+temperatures $T_1$ and $T_2$, in the simple demo problem.
+These are for the one-dimensional case, but
+in this example, the 100 dimensional canonical distributions are `independent
+and identically distributed' version of this distribution.
+Low values of $T_1$ bring
+more probability towards the centre of the domain, and low values of $T_2$
+bring out the oscillatory structure in the probability density function.
+\label{fig:demo_canonical}}
 \end{figure}
 
-% The MDPI table float is called specialtable
-\begin{specialtable}[H] 
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
-%%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
-\begin{tabular}{ccc}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data\\
-\bottomrule
-\end{tabular}
-\end{specialtable}
+\begin{figure}[!ht]
+\centering
+\includegraphics[scale=0.6]{figures/demo_truth.pdf}
+\caption{The true partition function and KL divergence (from the prior to
+the canonical distribution) as a function of two temperatures for the
+test problem.\label{fig:demo_truth}}
+\end{figure}
 
-%\begin{listing}[H]
-%\caption{Title of the listing}
-%\rule{\columnwidth}{1pt}
-%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
-%\rule{\columnwidth}{1pt}
-%\end{listing}
+The algorithm was run for 1000 reps, to a `depth' of 500 nats,
+with 100 particles and 1000 MCMC steps per NS iteration per rep.
+Results are given in
+Figures~\ref{fig:demo_logZ_H},~\ref{fig:demo_residuals},
+and~\ref{fig:demo_N_eff}.
 
-Text.
+\begin{figure}[!ht]
+\centering
+\includegraphics[scale=0.6]{figures/demo_logZ_H.pdf}
+\caption{The partition function $\ln(Z)$ and information $H$ as a function
+of the two temperatures, reconstructed using the algorithm. Compare with
+Figure~\ref{fig:demo_truth}.
+\label{fig:demo_logZ_H}}
+\end{figure}
 
-Text.
+\begin{figure}[!ht]
+\centering
+\includegraphics[scale=0.6]{figures/demo_residuals.pdf}
+\caption{The residuals, i.e., the difference between
+Figures~\ref{fig:demo_logZ_H} and~\ref{fig:demo_truth}.
+\label{fig:demo_residuals}}
+\end{figure}
 
-\subsection{Formatting of Mathematical Components}
+\begin{figure}[!ht]
+\centering
+\includegraphics[scale=0.6]{figures/demo_N_eff.pdf}
+\caption{The error in $\ln(Z)$, expressed in terms of an
+`effective number of particles' in a standard NS run that would lead to
+the same error at 1 sigma. No values are below $N_{\rm eff} = 1$.
+\label{fig:demo_N_eff}}
+\end{figure}
 
-This is the example 1 of equation:
-\begin{equation}
-a = 1,
-\end{equation}
-the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=1]{figures/output.png}
+%\caption{The sequence of discarded particles (yellow) and
+%points representing the canonical distribution at temperatures
+%$(T_1, T_2) = (0.1, 1)$ (black).\label{fig:output}}
+%\end{figure}
 
-This is the example 2 of equation:
-\end{paracol}
-\nointerlineskip
-\begin{equation}
-a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
-\end{equation}
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=0.5]{figures/results.pdf}
+%\caption{Numerical results for the test problem. These compare well with the
+%true partition function and KL divergence given in Figure~\ref{fig:truth}.
+%\label{fig:results}}
+%\end{figure}
 
-% Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, \linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.
-\begin{figure}[H]	
-\widefigure
-\includegraphics[width=15 cm]{Definitions/logo-mdpi}
-\caption{This is a wide figure.\label{fig2}}
-\end{figure}  
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
+\section{Example 2: Lennard-Jones/Polymer Example}
 
-Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
+Consider $n$ Lennard-Jones atoms confined to the unit cube $[0, 1]^3$.
+The position of each atom is given by a vector
+$\boldsymbol{r}_i = (x_i, y_i, z_i)$.
+The potential energy of any configuration of the atoms is given by
+a sum over all pairs of atoms:
+\begin{eqnarray}
+U_{\rm LJ} &=& \sum_{i=1}^n\sum_{j=(i+1)}^n U_{\rm LJ}
+(\boldsymbol{r}_i, \boldsymbol{r}_j)
+\end{eqnarray}
+where the inter-atomic potential energy is given by:
 
-The text continues here. Proofs must be formatted as follows:
+\begin{eqnarray}
+U_{\rm LJ}(\boldsymbol{r}_i, \boldsymbol{r}_j)
+&=& 4\epsilon
+\left[
+\left(\frac{\sigma}{|\boldsymbol{r}_i - \boldsymbol{r}_j|}\right)^12 -
+\left(\frac{\sigma}{|\boldsymbol{r}_i - \boldsymbol{r}_j|}\right)^6
+\right].
+\end{eqnarray}
+We adopted the Lennard Jones units by setting $\epsilon=1$ and $\sigma=1$.
 
-%% Example of a proof:
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
-\end{proof}
-The text continues here.
+In terms of the Lennard Jones parameters $\epsilon$ and $\sigma$, the
+``polymer'' potential is
+\begin{eqnarray}
+U_{\rm polymer} &=&
+\sum_{i=1}^{n-1} \phi^{(1)}_{i,i+1} + \sum_{i=2}^{n-1} \phi^{(2)}_{i-1, i, i+1}
+\end{eqnarray}
+where
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-
-Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Patents}
-
-This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
+\begin{eqnarray}
+\phi^{(1)}_{i,i+1} &=& \frac{k}{2}\left(|\boldsymbol{r}_i - \boldsymbol{r}_{i+1}|- 2^{1/6}\sigma\right)^2,\\
+\phi^{(2)}_{i-1, i, i+1} &=& \frac{k}{2}
+\left((\boldsymbol{r}_i - \boldsymbol{r}_{i-1})\cdot(\boldsymbol{r}_{i-1} - \boldsymbol{r}_{i}) - 1\right)^2,
+\end{eqnarray}
+and $k=\frac{36 \times 2^{2/3}\epsilon}{\sigma^2}$ has been chosen to match
+the curvature of $U_{\rm LJ}(\boldsymbol{r}_i, \boldsymbol{r}_j)$.
 
@@
 %=====================================
-%\externalbibliography{yes}
-%\bibliography{your_external_BibTeX_file}
+\externalbibliography{yes}
+\bibliography{references.bib/references}
 
@@
 %=====================================
-\begin{thebibliography}{999}
-% Reference 1
-\bibitem[Author1(year)]{ref-journal}
-Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
-% Reference 2
-\bibitem[Author2(year)]{ref-book1}
-Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-% Reference 3
-\bibitem[Author3(year)]{ref-book2}
-Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
-% Reference 4
-\bibitem[Author4(year)]{ref-unpublish}
-Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} stage of publication (under review; accepted; in~press).
-% Reference 5
-\bibitem[Author5(year)]{ref-communication}
-Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
-% Reference 6
-\bibitem[Author6(year)]{ref-proceeding}
-Author 1, A.B.; Author 2, C.D.; Author 3, E.F.
-Title of Presentation.
-In Title of the Collected Work (if available), Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference; Editor 1, Editor 2, Eds.
-(if available); Publisher: City, Country, Year (if available); Abstract Number (optional), Pagination (optional).
-% Reference 7
-\bibitem[Author7(year)]{ref-thesis}
-Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
-% Reference 8
-\bibitem[Author8(year)]{ref-url}
-Title of Site. Available online: URL (accessed on Day Month Year).
-\end{thebibliography}
 

### 2021-05-17 include/Constants.h
Use historical example

@@ -7,9 +7,9 @@ namespace Forklift
 namespace Constants
 {
 
-    static constexpr int num_particles = 100;
+    static constexpr int num_particles = 30;
     static constexpr int mcmc_steps = 1000;
-    static constexpr int depth_nats = 100;
+    static constexpr int depth_nats = 500;
     static constexpr double thin = 0.1;
 
 } // namespace Constants

### 2021-05-17 include/Examples/Demo.hpp

@@ -14,7 +14,7 @@ namespace Examples
 class Demo
 {
     private:
-        static constexpr int size = 20;
+        static constexpr int size = 100;
         std::vector<double> params;
 
     public:
@@ -55,7 +55,7 @@ double Demo::x() const
 {
     double f = 0.0;
     for(double value: params)
-        f += -0.5*1E4*pow(value - 0.5, 2);
+        f += -1E2*pow(value - 0.5, 2);
     return f;
 }
 
@@ -63,7 +63,7 @@ double Demo::y() const
 {
     double g = 0.0;
     for(double value: params)
-        g += -1E2*value;
+        g += -pow(sin(10.0*M_PI*value), 2);
     return g;
 }
 

### 2021-05-17 include/StripeImpl.h

@@ -33,6 +33,7 @@ void Stripe<M>::ns_iteration(Database& database, Tools::RNG& rng)
     ++iteration;
 
     std::cout << "Stripe " << stripe_id << ", iteration " << iteration;
+    std::cout << '/' << Constants::num_particles*Constants::depth_nats;
     std::cout << ':' << std::endl;
 
     // Find worst particle

### 2021-05-17 paper/figures.py

@@ -1,0 +1,49 @@
+import matplotlib.pyplot as plt
+import numpy as np
+#import twinpeaks2018 as tp
+
+## Set up the fonts
+#tp.plot_settings()
+
+## Compute the true partition function
+#limits = [1E-1, 1E2, 1E-1, 1E2]
+#truth = tp.demo_truth.compute_truth(limits=limits, n=51)
+
+## Plot the results
+#plt.figure(1, figsize=(9, 6))
+#plt.subplot(1, 2, 1)
+#plt.imshow(truth["ln_Z"], origin="lower", extent=np.log10(limits))
+#plt.xlabel("$\\log_{10}(T_1)$")
+#plt.ylabel("$\\log_{10}(T_2)$")
+#plt.title("$\\ln(Z)$")
+
+#plt.subplot(1, 2, 2)
+#plt.imshow(truth["H"], origin="lower", extent=np.log10(limits))
+#plt.xlabel("$\\log_{10}(T_1)$")
+#plt.title("$H$")
+
+#plt.savefig("figures/demo_truth.pdf")
+#print("Saved figures/demo_truth.pdf")
+
+x = np.linspace(0.0, 1.0, 1001)
+def s(x, T1, T2):
+    s = -((x - 0.5)/0.1)**2/T1 - np.sin(10.0*np.pi*x)**2/T2
+    return np.exp(s)
+
+plt.figure(2, figsize=(7, 6))
+plt.rcParams["font.size"] = 14
+S = s(x, 10.0, 10.0)
+S = S / np.trapz(S, x=x)
+plt.plot(x, S, label="$(T_1, T_2) = (1, 1)$")
+S = s(x, 10.0, 1.0)
+S = S / np.trapz(S, x=x)
+plt.plot(x, S, label="$(T_1, T_2) = (10, 1)$")
+S = s(x, 1.0, 10.0)
+S = S / np.trapz(S, x=x)
+plt.plot(x, S, label="$(T_1, T_2) = (1, 10)$")
+plt.xlabel("$x$")
+plt.ylabel("$p(x; T_1, T_2)$")
+plt.legend()
+plt.savefig("figures/demo_canonical.pdf")
+print("Saved figures/demo_canonical.pdf")
+

### 2021-05-17 showresults.py

@@ -35,10 +35,10 @@ def _canonical_grid(limits, xs, ys, logws, num, resid):
             info = np.sum(ps*(logls - logz))
             if resid:
                 x = np.linspace(0.0, 1.0, 20001)
-                y = np.exp(-0.5*1E4*(x - 0.5)**2/Tx[j] - 1E2*x/Ty[i])
+                y = np.exp(-1E2*(x - 0.5)**2/Tx[j] - np.sin(10.0*np.pi*x)**2/Ty[i])
                 p = y/np.trapz(y, x=x)
-                logz -= 20.0*np.log(np.trapz(y, x=x))
-                info -= 20.0*np.trapz(p*np.log(p + 1E-300), x=x)
+                logz -= 100.0*np.log(np.trapz(y, x=x))
+                info -= 100.0*np.trapz(p*np.log(p + 1E-300), x=x)
             logzs_infos[0, i, j] = logz
             logzs_infos[1, i, j] = info
             logzs_infos[2, i, j] = np.sum(ps*xs)
@@ -151,12 +151,12 @@ class Results:
 
 
 results = Results()
-print(results.logz_and_info((20.0, 1.0)))
+#print(results.logz_and_info((20.0, 1.0)))
 
 results.plot_scalars()
 
 # Extent for canonical distributions
-limits = [1.0, 100.0, 1.0, 100.0]
+limits = [0.1, 100.0, 0.1, 100.0]
 num = 51
 resid = False
 logzs_infos = results.canonical_grid(limits, num, resid)
@@ -170,12 +170,20 @@ cmap = "coolwarm" if resid else "viridis"
 
 plt.figure(figsize=(8, 8))
 plt.subplot(2, 2, 1)
-plt.imshow(logzs_infos[0, :, :], extent=extent, cmap=cmap)
+vmin, vmax = None, None
+if resid:
+    vmin = -np.max(np.abs(logzs_infos[0, :, :]))
+    vmax = np.abs(vmin)
+plt.imshow(logzs_infos[0, :, :], extent=extent, cmap=cmap, vmin=vmin, vmax=vmax)
 plt.ylabel("$\\log_{10}\\left(T_y\\right)$")
 plt.title("$\\log Z$")
 
 plt.subplot(2, 2, 2)
-plt.imshow(logzs_infos[1, :, :], extent=extent, cmap=cmap)
[…]

### 2021-05-18 display_potts.py
Potts!

@@ -1,0 +1,30 @@
+import apsw
+import matplotlib.pyplot as plt
+import numpy as np
+import os
+
+conn = apsw.Connection("output/forklift.db", flags=apsw.SQLITE_OPEN_READONLY)
+db = conn.cursor()
+
+os.system("rm output/potts*")
+
+i = 0
+plt.figure(figsize=(7, 7))
+for row in db.execute("SELECT stripe_id, iteration, params\
+                        FROM particles\
+                        WHERE params IS NOT NULL;"):
+    stripe, iteration, params = row
+    num_bytes = len(params)
+    pixels = np.frombuffer(params, dtype=np.int32)
+    pixels = pixels.reshape((32, 32))
+
+    plt.clf()
+    plt.imshow(pixels, vmin=0, vmax=5)
+    plt.title(f"Stripe {stripe}, iteration {iteration}.")
+    fname = "output/potts" + "%0.6d" % (i + 1) + ".png"
+    plt.savefig(fname)
+    print(f"Saved {fname}.", flush=True)
+    i += 1
+
+os.system("ffmpeg -r 10 -i output/potts%06d.png -c:v libx264 -b:v 5M output/potts.mp4")
+

### 2021-05-18 include/Examples/Potts.hpp

@@ -1,0 +1,196 @@
+#ifndef Forklift_Examples_Potts_hpp
+#define Forklift_Examples_Potts_hpp
+
+#include <Tools/Misc.hpp>
+#include <Tools/RNG.hpp>
+#include <vector>
+
+namespace Forklift
+{
+
+namespace Examples
+{
+
+class Potts
+{
+	private:
+		static constexpr int num_colors = 5;
+        static constexpr int n = 32;
+
+        // State
+		std::vector<std::vector<int>> pixels;
+        std::vector<double> s_values;
+
+		// So we can just update on the fly
+		int score;
+		int score2;
+
+		void compute_score();
+		void compute_scalars();
+
+	public:
+
+		Potts() = delete;
+        Potts(Tools::RNG& rng);
+		double perturb(Tools::RNG& rng);
+        std::vector<double> scalars() const;
+        double x() const;
+        double y() const;
+        std::vector<unsigned char> to_bytes() const;
+
+};
+
+/* IMPLEMENTATIONS FOLLOW */
+
+
+Potts::Potts(Tools::RNG& rng)
+:pixels(n, std::vector<int>(n))
+,s_values(2)
+{
+	for(size_t i=0; i<pixels.size(); i++)
+		for(size_t j=0; j<pixels[i].size(); j++)
+			pixels[i][j] = rng.rand_int(num_colors);
+
+	compute_score();
+	compute_scalars();
+}
+
+void Potts::compute_score()
+{
+	score = 0;
+	score2 = 0;
+
+	// Coordinates of neighbouring cells
+	std::vector<int> ii(4);
+    std::vector<int> jj(4);
+
+	for(size_t i=0; i<pixels.size(); i++)
+	{
+		for(size_t j=0; j<pixels[i].size(); j++)
+		{
+			for(int k=0; k<4; k++)
+			{
+				ii[k] = i;
+				jj[k] = j;
+			}
+
+			// Down, up, right, left
+			ii[0] = Tools::mod(i + 1, static_cast<int>(pixels.size()));
+			ii[1] = Tools::mod(i - 1, static_cast<int>(pixels.size()));
+			jj[2] = Tools::mod(j + 1, static_cast<int>(pixels[i].size()));
+			jj[3] = Tools::mod(j - 1, static_cast<int>(pixels[i].size()));
+
+			for(int k=0; k<4; k++)
+			{
[…]

### 2021-05-18 showresults.py
Thin for plotting if needed

@@ -131,11 +131,15 @@ class Results:
         self.logws, self.xs, self.ys = logws, xs, ys
 
     def plot_scalars(self):
-        if len(self.xs) > 1E6:
-            print("Skipping plot because there are too many points.")
-            return
+        xs, ys = self.xs, self.ys
 
-        plt.plot(self.xs, self.ys, ".", markersize=1, alpha=0.3)
+        if len(xs) > 1E6:
+            prob = 1E6/len(xs)
+            keep = rng.rand(len(xs)) < prob
+            xs = xs[keep]
+            ys = ys[keep]
+
+        plt.plot(xs, ys, ".", markersize=2, alpha=0.3)
         plt.show()
 
     def logz_and_info(self, temperatures):

### 2021-05-19 paper/ms.tex
Use historical example
Do Atoms and Potts

@@
 \usepackage{dsfont}
+\usepackage{algorithm2e}
 \newcommand{\xx}{\boldsymbol{\theta}}
@@
 temperatures) is known, so we can compute the actual error in the reconstructed
-function $Z(\beta_1, \beta_2)$; (ii) a collection of atoms with a potential
-that is intermediate between a Lennard-Jones form and a `polymer' form; and
-(iii) {\todo decide between a few options: image reconstruction with an
-intractable normalizing constant in the prior, or perhaps the `Potts' example
+function $Z(\beta_1, \beta_2)$; (ii) Lennard-Jones atoms in an external field;
+and
+(iii) a `Potts' example
 which is a compromize between a 2D potts model and a product of many 1D
-Potts models}.
+Potts models.
 A free software implementation in modern C++ is available at

### 2021-05-19 paper/ms.tex
A paragraph

@@
 performance is those cases is likely to be poor).
+
+\section{NS with respect to one scalar}
+Consider a simple problem where the parameter space is two dimensional,
+the prior is
+\begin{align}
+x &\sim \textnormal{Exponential}(1) \\
+y &\sim \textnormal{Exponential}(1),
+\end{align}
+and the two objective functions are also just $x$ and $y$ themselves.
+If we were to run standard Nested Sampling on this problem, targeting
+$x$, we would end up with points uniformly distributed along $x$ and
+exponentially distributed along $y$ (in a frequency sense, with very high
+prior probability).
 

### 2021-05-20 include/Config.h
Replace Constants with Config

@@ -1,0 +1,20 @@
+#ifndef Forklift_Config_h
+#define Forklift_Config_h
+
+namespace Forklift
+{
+
+// A singleton
+struct Config
+{
+    static int num_particles;
+    static int mcmc_steps;
+    static int depth_nats;
+    static double thin;
+    static void load(const char* filename);
+};
+
+
+} // namespace
+
+#endif

### 2021-05-20 include/Constants.h

@@ -1,20 +1,0 @@
-#ifndef Forklift_Constants_h
-#define Forklift_Constants_h
-
-namespace Forklift
-{
-
-namespace Constants
-{
-
-    static constexpr int num_particles = 30;
-    static constexpr int mcmc_steps = 1000;
-    static constexpr int depth_nats = 500;
-    static constexpr double thin = 0.1;
-
-} // namespace Constants
-
-} // namespace
-
-#endif
-

### 2021-05-20 include/Database.h

@@ -1,7 +1,7 @@
 #ifndef Forklift_Database_h
 #define Forklift_Database_h
 
-#include "Constants.h"
+#include "Config.h"
 #include "Double.h"
 #include <optional>
 #include <sqlite_modern_cpp/hdr/sqlite_modern_cpp.h>

### 2021-05-20 include/SamplerImpl.h

@@ -1,7 +1,7 @@
 #ifndef Forklift_SamplerImpl_h
 #define Forklift_SamplerImpl_h
 
-#include "Constants.h"
+#include "Config.h"
 #include <iostream>
 #include <Tools/Misc.hpp>
 
@@ -17,10 +17,10 @@ Sampler<M>::Sampler(Tools::RNG&& _rng)
 {
     std::cout << "Generating particles from the prior..." << std::flush;
 
-    particles.reserve(Constants::num_particles);
-    xs.reserve(Constants::num_particles);
-    ys.reserve(Constants::num_particles);
-    for(int i=0; i<Constants::num_particles; ++i)
+    particles.reserve(Config::num_particles);
+    xs.reserve(Config::num_particles);
+    ys.reserve(Config::num_particles);
+    for(int i=0; i<Config::num_particles; ++i)
     {
         M m{rng};
         xs.emplace_back(m.x(), rng);
@@ -37,14 +37,13 @@ void Sampler<M>::update()
 {
     // Create stripe and ascend
     Stripe<M> stripe(stripe_id, particles, xs, ys, xstar);
-    int stripe_iterations = Constants::num_particles
-                                        *(Constants::depth_nats - 0); //stripe_id);
+    int stripe_iterations = Config::num_particles*Config::depth_nats;
     for(int i=0; i<stripe_iterations; ++i)
         stripe.ns_iteration(database, rng);
 
     ++stripe_id;
 
-    for(int i=0; i<Constants::num_particles; ++i)
+    for(int i=0; i<Config::num_particles; ++i)
         ns_iteration();
 
     // Clear out particles
@@ -94,7 +93,7 @@ void Sampler<M>::ns_iteration()
     int& k = worst;
 
     int accepted = 0;
-    for(int i=0; i<Constants::mcmc_steps; ++i)
+    for(int i=0; i<Config::mcmc_steps; ++i)
     {
         M proposal = particles[k];
         double logh = proposal.perturb(rng);
@@ -114,7 +113,7 @@ void Sampler<M>::ns_iteration()
     }
 
     std::cout << "done. ";
-    std::cout << "Accepted " << accepted << '/' << Constants::mcmc_steps << ' ';
+    std::cout << "Accepted " << accepted << '/' << Config::mcmc_steps << ' ';
     std::cout << "proposals.\n" << std::endl;
 }
 

### 2021-05-20 include/StripeImpl.h

@@ -1,7 +1,7 @@
 #ifndef Forklift_StripeImpl_h
 #define Forklift_StripeImpl_h
 
-#include <Constants.h>
+#include "Config.h"
 #include <iostream>
 #include <Tools/Misc.hpp>
 
@@ -33,7 +33,7 @@ void Stripe<M>::ns_iteration(Database& database, Tools::RNG& rng)
     ++iteration;
 
     std::cout << "Stripe " << stripe_id << ", iteration " << iteration;
-    std::cout << '/' << Constants::num_particles*Constants::depth_nats;
+    std::cout << '/' << Config::num_particles*Config::depth_nats;
     std::cout << ':' << std::endl;
 
     // Find worst particle
@@ -46,7 +46,7 @@ void Stripe<M>::ns_iteration(Database& database, Tools::RNG& rng)
 
     // Save worst particle
     std::optional<std::vector<unsigned char>> bytes;
-    if(rng.rand() <= Constants::thin)
+    if(rng.rand() <= Config::thin)
         bytes = particles[worst].to_bytes();
 
     database.save_particle(stripe_id, iteration, bytes,
@@ -81,7 +81,7 @@ void Stripe<M>::ns_iteration(Database& database, Tools::RNG& rng)
     int& k = worst;
 
     int accepted = 0;
-    for(int i=0; i<Constants::mcmc_steps; ++i)
+    for(int i=0; i<Config::mcmc_steps; ++i)
     {
         M proposal = particles[k];
         double logh = proposal.perturb(rng);
@@ -101,7 +101,7 @@ void Stripe<M>::ns_iteration(Database& database, Tools::RNG& rng)
     }
 
     std::cout << "done. ";
-    std::cout << "Accepted " << accepted << '/' << Constants::mcmc_steps << ' ';
+    std::cout << "Accepted " << accepted << '/' << Config::mcmc_steps << ' ';
     std::cout << "proposals.\n" << std::endl;
 }
 

### 2021-05-20 main.cpp

@@ -1,5 +1,5 @@
 #include <iostream>
-#include <Constants.h>
+#include "Config.h"
 #include <Examples/Demo.hpp>
 #include <Sampler.h>
 
@@ -7,9 +7,9 @@ using namespace Forklift;
 
 int main()
 {
+    Config::load("config.yaml");
     Sampler<Examples::Demo> sampler{Tools::RNG()};
-
-    for(int i=0; i<Constants::depth_nats; ++i)
+    for(int i=0; i<Config::depth_nats; ++i)
         sampler.update();
 
     return 0;

### 2021-05-20 src/Config.cpp

@@ -1,0 +1,21 @@
+#include "Config.h"
+#include <yaml-cpp/yaml.h>
+
+namespace Forklift
+{
+
+int Config::num_particles = 30;
+int Config::mcmc_steps = 1000;
+int Config::depth_nats = 100;
+double Config::thin = 0.1;
+
+void Config::load(const char* filename)
+{
+    YAML::Node node = YAML::LoadFile(filename);
+    num_particles = node["num_particles"].as<int>();
+    mcmc_steps = node["mcmc_steps"].as<int>();
+    depth_nats = node["depth_nats"].as<int>();
+    thin = node["thin"].as<double>();
+}
+
+} // namespace

### 2021-05-20 src/Database.cpp

@@ -50,7 +50,7 @@ CREATE TABLE IF NOT EXISTS constants\n\
  mcmc_steps    INTEGER NOT NULL);";
 
     db << "INSERT OR IGNORE INTO constants VALUES (1, ?, ?);"
-       << Constants::num_particles << Constants::mcmc_steps;
+       << Config::num_particles << Config::mcmc_steps;
 
 
     db << "\n\

### 2021-05-20 include/Config.h
RNG seed in config file

@@ -11,9 +11,9 @@ struct Config
     static int mcmc_steps;
     static int depth_nats;
     static double thin;
+    static int rng_seed;
     static void load(const char* filename);
 };
-
 
 } // namespace
 

### 2021-05-20 main.cpp

@@ -8,7 +8,7 @@ using namespace Forklift;
 int main()
 {
     Config::load("config.yaml");
-    Sampler<Examples::Demo> sampler{Tools::RNG()};
+    Sampler<Examples::Demo> sampler{Tools::RNG(Config::rng_seed)};
     for(int i=0; i<Config::depth_nats; ++i)
         sampler.update();
 

### 2021-05-20 src/Config.cpp

@@ -8,6 +8,7 @@ int Config::num_particles = 30;
 int Config::mcmc_steps = 1000;
 int Config::depth_nats = 100;
 double Config::thin = 0.1;
+int Config::rng_seed = 0;
 
 void Config::load(const char* filename)
 {
@@ -16,6 +17,15 @@ void Config::load(const char* filename)
     mcmc_steps = node["mcmc_steps"].as<int>();
     depth_nats = node["depth_nats"].as<int>();
     thin = node["thin"].as<double>();
+
+    try
+    {
+        rng_seed = node["rng_seed"].as<int>();
+    }
+    catch(...)
+    {
+        rng_seed = time(0);
+    }
 }
 
 } // namespace

### 2021-05-20 src/Database.cpp

@@ -47,11 +47,11 @@ void Database::create_tables()
 CREATE TABLE IF NOT EXISTS constants\n\
 (id            INTEGER NOT NULL PRIMARY KEY,\n\
  num_particles INTEGER NOT NULL,\n\
- mcmc_steps    INTEGER NOT NULL);";
+ mcmc_steps    INTEGER NOT NULL,\n\
+ rng_seed      INTEGER NOT NULL);";
 
-    db << "INSERT OR IGNORE INTO constants VALUES (1, ?, ?);"
-       << Config::num_particles << Config::mcmc_steps;
-
+    db << "INSERT OR IGNORE INTO constants VALUES (1, ?, ?, ?);"
+       << Config::num_particles << Config::mcmc_steps << Config::rng_seed;
 
     db << "\n\
 CREATE TABLE IF NOT EXISTS particles\n\

### 2021-05-20 include/Config.h
Two depths

@@ -1,6 +1,8 @@
 #ifndef Forklift_Config_h
 #define Forklift_Config_h
 
+#include <tuple>
+
 namespace Forklift
 {
 
@@ -9,7 +11,7 @@ struct Config
 {
     static int num_particles;
     static int mcmc_steps;
-    static int depth_nats;
+    static std::pair<int, int> depth_nats;
     static double thin;
     static int rng_seed;
     static void load(const char* filename);

### 2021-05-20 include/SamplerImpl.h

@@ -37,7 +37,7 @@ void Sampler<M>::update()
 {
     // Create stripe and ascend
     Stripe<M> stripe(stripe_id, particles, xs, ys, xstar);
-    int stripe_iterations = Config::num_particles*Config::depth_nats;
+    int stripe_iterations = Config::num_particles*std::get<1>(Config::depth_nats);
     for(int i=0; i<stripe_iterations; ++i)
         stripe.ns_iteration(database, rng);
 

### 2021-05-20 include/StripeImpl.h

@@ -33,7 +33,7 @@ void Stripe<M>::ns_iteration(Database& database, Tools::RNG& rng)
     ++iteration;
 
     std::cout << "Stripe " << stripe_id << ", iteration " << iteration;
-    std::cout << '/' << Config::num_particles*Config::depth_nats;
+    std::cout << '/' << Config::num_particles*std::get<1>(Config::depth_nats);
     std::cout << ':' << std::endl;
 
     // Find worst particle

### 2021-05-20 main.cpp

@@ -9,7 +9,7 @@ int main()
 {
     Config::load("config.yaml");
     Sampler<Examples::Demo> sampler{Tools::RNG(Config::rng_seed)};
-    for(int i=0; i<Config::depth_nats; ++i)
+    for(int i=0; i<std::get<0>(Config::depth_nats); ++i)
         sampler.update();
 
     return 0;

### 2021-05-20 src/Config.cpp

@@ -6,7 +6,7 @@ namespace Forklift
 
 int Config::num_particles = 30;
 int Config::mcmc_steps = 1000;
-int Config::depth_nats = 100;
+std::pair<int, int> Config::depth_nats = {100, 100};
 double Config::thin = 0.1;
 int Config::rng_seed = 0;
 
@@ -15,7 +15,8 @@ void Config::load(const char* filename)
     YAML::Node node = YAML::LoadFile(filename);
     num_particles = node["num_particles"].as<int>();
     mcmc_steps = node["mcmc_steps"].as<int>();
-    depth_nats = node["depth_nats"].as<int>();
+    depth_nats = {node["depth_nats"][0].as<int>(),
+                  node["depth_nats"][1].as<int>()};
     thin = node["thin"].as<double>();
 
     try

### 2021-05-21 include/Examples/All.hpp
Include all examples

@@ -1,0 +1,8 @@
+#ifndef Forklift_Examples_All_hpp
+#define Forklift_Examples_All_hpp
+
+#include "Atoms.hpp"
+#include "Demo.hpp"
+#include "Potts.hpp"
+
+#endif

### 2021-05-21 main.cpp

@@ -1,6 +1,6 @@
 #include <iostream>
 #include "Config.h"
-#include <Examples/Demo.hpp>
+#include <Examples/All.hpp>
 #include <Sampler.h>
 
 using namespace Forklift;

### 2021-05-21 include/StripeImpl.h
Print depth

@@ -34,6 +34,8 @@ void Stripe<M>::ns_iteration(Database& database, Tools::RNG& rng)
 
     std::cout << "Stripe " << stripe_id << ", iteration " << iteration;
     std::cout << '/' << Config::num_particles*std::get<1>(Config::depth_nats);
+    std::cout << " (depth ~= " << double(iteration)/Config::num_particles
+              << " nats)";
     std::cout << ':' << std::endl;
 
     // Find worst particle
